---
title: "PredatorPreySim1"
author: "Justin Mann"
date: "2023-10-04"
output: html_document
runtime: shiny
---

```{r}
```{r runSim, echo=FALSE}

beginSim <- function(camiPop, pollPop, camiPopMultiply, numGenerations, printArray, printLocations) {
  # Your simulation logic goes here
  # Perform simulations based on the input parameters
  # You can modify this function according to your simulation requirements
  
  # For example, a simple simulation might involve iterating over generations and updating populations
  for (i in 1:numGenerations) {
    # Update populations based on reproduction rates
    camiPop <- camiPop * camiPopMultiply
    pollPop <- pollPop * 1.2 # Assuming a fixed reproduction rate for Pollards
    
    # Print populations if printArray is TRUE
    if (printArray) {
      print(camiPop, pollPop)
    }
    
    # Print coordinates if printLocations is TRUE
    if (printLocations) {
      print(paste("Generation", i, ": Caminalcule - X:", runif(1, 0, 100), "Y:", runif(1, 0, 100),
                  "Pollard - X:", runif(1, 0, 100), "Y:", runif(1, 0, 100)))
    }
  }
  
  # Return simulation results, you can modify this according to your simulation logic
  return(list(camiPop = camiPop, pollPop = pollPop))
}


```

